Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-03-28 Latex/draft.tex
syncing
Added footnote to draft for corsi, fenwick.

In addition to model research, some research has also gone into developing new features that can be used to better predict the game outcomes. 
The two biggest engineered classes of features are the Corsi (\url{https://en.wikipedia.org/wiki/Corsi_(statistic)})
 and Fenwick (\url{https://en.wikipedia.org/wiki/Fenwick_(statistic)}) metrics (both from 2007).

>>>>

In addition to model research, some research has also gone into developing new features that can be used to better predict the game outcomes. 
The two biggest engineered classes of features are the Corsi
 and Fenwick\footnote{These metrics were created by sports bloggers Tim Barnes and Mark Fenwick, respectively. 
 We were unable to locate the original blog posts talking about these metrics, but a good article to learn more about the math can be
 found here \url{https://thehockeywriters.com/corsi-fenwick-stats-what-are-they/}.} metrics (both around 2007).
